Tropical Andes plant checklist using GIFT

### 2023-10-18 code/L0/L0_TropicalAndes_plants_checklist.Rmd
add summary and save to csv code

>>>>

```{r}
print("The number of species is")
length(unique(checklist$checklists$work_species))
print("The number of families is")
length(unique(checklist$checklists$family))
```

# Write data to csv
```{r}
write.csv(checklist$checklists, file = file.path(output_path,"TropicalAndes_plant_checklist.csv"))
```
